SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-02 design_arch.tex
Updated results section & added graphs
added more general intro

\section{PPF Architecture}
\label{Arch}

In this section, we talk about the the general structure of the 
Perceptron-Based Prefetch Filtering (PPF) for enhancing an underlying prefetcher.  
PPF is a generalised prefetch filtering mechanism and can be adapted to 
most prefetchers with minimal modifications. %Gino: Are these modifications minimal?

\subsection{The Perceptron Filter}
\label{Arch-Perceptron}
The Perceptron Filter is organized as tables of perceptron weights, 
with a separate table of weights for each feature.  
A different number of bits are used for each feature to index into its 
corresponding table.
%Gino: repharse below?
Each feature's value is used to index into the corresponding table.
This indexing is done using a different number of bits for each feature.  
At most, 12 bits of a feature are used to index into the
weights table. Certain features require more resolution
\textit{i.e.}, the full 12 bits of indexing.  On the other hand, some
features requiring lower resolution require as few as 7 bits of indexing. 
The variable indexing was determined by studying the
features and fine-tuned empirically to achieve a good accuracy
vs hardware overhead trade-off.  Exact details are mentioned under ``Area Overheads''
in Section~\ref{Method-Overheads}

@@

When the base prefetcher is triggered, it begins to suggest candidates for
prefetching. All suggested prefetches are passed through the perceptron
filter to decide if they are qualified for final prefetching. 
he perceptron decides whether to prefetch a candidate by looking at the microarchitectural state 
\em} i.e. the features, at that instant. Each feature is hashed to form an index into a table of up to 
4096 entries dedicated for that feature.

>>>>

\section{PPF Design and Architecture}
\label{Arch}
% Really need a high-level overview of the technique before you start
% talking about tables!

As previously discussed, ultimately it might be profitable to allow a
given prefetcher to speculate as deeply as possible, since often some
useful prefetches are still being generated long after the confidence
of the prefetcher has fallen below the point at which performance
improvements are seen, due to the increasing rate of inaccurate
prefetches.  In order to allow this deep speculation in the
prefetcher, however, the increasing numbers of bad prefetches must be
filtered out.  To this end, we propose to leverage perceptron-based
machine learning as a mechanism to differentiate between potentially
useful deeply speculated prefetches and likely not-useful ones.  This
Perceptron Prefetch Filter (PPF) is placed between the prefetcher and
the prefetch insertion queue, to ensure that predicted bad prefetches
are not inserted into the memory system, \pg{As shown in figure
  whatever...}.

As discussed in Section~\ref{sec:Background-Perceptron}, perceptrons
are useful, light-weight mechanisms to pull together disparate forms
of information and synthesize a decision from them.  In this case, we
will leverage a variety of different relative characteristics of a
given prefetch, such as speculation depth, page address and offset,
into a binary useful/non-useful prediction.  In the remainder of this
section, we discus the the general structure of PPF for enhancing a
given underlying prefetcher.  We will show that PPF is a generalized
prefetch filtering mechanism which may adapted to any prefetcher with
minimal modifications. %Gino: Are these modifications minimal?

\subsection{The Perceptron Filter}
\label{Arch-Perceptron}

The Perceptron Filter is organized as tables of perceptron weights,
with a separate table of weights for each feature.  A different number
of bits are used for each feature to index into its corresponding
table.
%Gino: repharse below?
Each feature's value is used to index into the corresponding table.
This indexing is done using a different number of bits for each
feature.  At most, 12 bits of a feature are used to index into the
weights table. Certain features require more resolution \textit{i.e.},
the full 12 bits of indexing.  On the other hand, some features
requiring lower resolution require as few as 7 bits of indexing.  The
variable indexing was determined by studying the features and
fine-tuned empirically to achieve a good accuracy vs hardware overhead
trade-off.  Exact details are mentioned under ``Area Overheads'' in
Section~\ref{Method-Overheads}

@@

When the base prefetcher is triggered, it begins to suggest candidates
for prefetching. All suggested prefetches are passed through the
perceptron filter to decide if they are qualified for final
prefetching.  The perceptron decides whether to prefetch a candidate
by looking at the microarchitectural state \textit{i.e.} the features,
at that instant. Each feature is hashed to form an index into a table
of up to 4096 entries dedicated for that feature.
